Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas

### 2021-04-14 analysis/paper/paper.Rmd
EXPLORE EXAMPLE DATA COLOR OPTIONS
there is a commented out section that relies on the latest viridisLite. But, no success or significatn improvement re: discerning variation in the lower values.

p <- ggplot(d,aes(day,hour,fill=percent_dry))+
  geom_tile(color= "white",size=0) + 
  scale_fill_viridis_c(name = "hourly percent dry", aesthetics = "fill",
    guide = guide_colorbar(title.position = "bottom", barwidth = 15, 
                           barheight = 0.5, title.hjust = 0.5)
    )
p <- p + facet_grid(year~month)
#p <- p + scale_y_continuous(trans = "reverse")
p <- p + scale_x_continuous(breaks = c(1,10,20,30))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  ggtitle("Observation records are incomplete because not all data is transmitted",
          subtitle = "percent-dry data for a single ribbon seal across two years") +
  xlab("day of month") + ylab("hour (UTC)")
p
```

>>>>

p <- ggplot(d,aes(day,hour,fill=percent_dry))+
  geom_tile(color= "white",size=0) + 
  # scale_fill_gradientn(colors = viridisLite::turbo(n=256),
  #                      name = "hourly percent dry", aesthetics = "fill",
  #   guide = guide_colorbar(title.position = "bottom", barwidth = 15, 
  #                          barheight = 0.5, title.hjust = 0.5)
  #   )
  scale_fill_viridis_c(name = "hourly percent dry", aesthetics = "fill",
    guide = guide_colorbar(title.position = "bottom", barwidth = 15,
                           barheight = 0.5, title.hjust = 0.5)
  )
p <- p + facet_grid(year~month)
#p <- p + scale_y_continuous(trans = "reverse")
p <- p + scale_x_continuous(breaks = c(1,10,20,30))
p <- p + theme(legend.position = "bottom") +
  theme(strip.background = element_rect(colour="white")) +
  theme(axis.ticks=element_blank()) +
  ggtitle("Observation records are incomplete because not all data is transmitted",
          subtitle = "percent-dry data for a single ribbon seal across two years") +
  xlab("day of month") + ylab("hour (UTC)")
p
```
